Towards automated provenance collection for experimental runs of agent-based models\thanks{This work was supported by the Scottish Government Rural and Environment Science and Analytical Services Division (project reference JHI-C5-1)}

### 2023-04-19 paper/paper.tex
Added the images that are the basis of the diagrams

\begin{figure} \includegraphics[width=\textwidth]{img/broken-application.pdf}
\caption{The workflow sub-graph} \label{fig:broken-application} \end{figure}

@@

\begin{figure} \includegraphics[width=\textwidth]{img/high-lit-provenance-trace.pdf}
\caption{The workflow sub-graph} \label{fig:high-lit-provenance-trace} \end{figure}

>>>>

\begin{figure} \includegraphics[width=\textwidth]{img/broken-application.pdf}
\caption{The workflow sub-graph show the propagation of a broken application (in red) to its outputs} \label{fig:broken-application} \end{figure}

@@

\begin{figure} \includegraphics[width=\textwidth]{img/high-lit-provenance-trace.pdf}
\caption{A provenance sub-graph showing (in red) the propagation of bad data through the system} \label{fig:high-lit-provenance-trace} \end{figure}
